Quantifying the global film festival circuit: networks, diversity and value creation

### 2023-03-01 cudan/paperplots.qmd
div

abcols=divergingx_hcl(6, palette="Zissou 1")[c(1,5)]
abshapes=c(16,4)

@@

  if(!splitab & !is.null(ex)){
   if(networkstats){
      fromy=2014.5; toy=2019.5
    } else{
      fromy=2008; toy=2022
      g=g+geom_errorbar(aes(ymin=lower, ymax=upper), color="gray40", width=0.1, size=0.45)
    }
    g=
      g+facet_wrap(~libelleFestival_NEW_VZ, nrow = length(ex)/6)+
      # geom_point( aes(YearEvent, target),data=vecs %>% select(-libelleFestival_NEW_VZ), inherit.aes = F,
      #             color="gray90", size=0.9)+
      geom_line(data=vex %>% filter(YearEvent>fromy, YearEvent<toy) %>% 
                  group_by(YearEvent, libelleFestival_NEW_VZ) %>% 
                  summarise(target=mean(target, na.rm=T), tool=NA, ab=ab[1]), 
                color="gray60", size=0.3
                )+
      geom_point(data=vex, alpha=1, size=1.5, shape=16)+
      scale_x_continuous(breaks=seq(2009,2021,3) )+
      scale_y_continuous(limits=c( min(vecs$target), max(vecs$target) ))+
      theme(
       panel.grid.major.x  = element_line(color="gray95"),
       panel.grid.minor.x  = element_blank(),
       legend.position = 'none'
       )
  }

@@

@@

# big force directed
gr = as_tbl_graph(graph_from_data_frame(e2, directed = F, vertices = nodelist %>% filter(EventID_VZ %in% c(e2$from,e2$to))))
g = ggraph(gr  ) +
  geom_node_point(aes(color=YearEvent, size=nf)) +
  #geom_node_text(aes(label=name)) +
  geom_edge_arc(aes(color=coloryear, alpha=dist),  width=0.1, strength=0.04) +
  scale_color_viridis(end=0.9)+
  scale_edge_color_viridis(end=0.9)+
  scale_edge_alpha(range=c(0.15, 0.5))+
  scale_size(0.5, 1.5)+
  theme_void()+
  theme(legend.position = 'none',
        plot.background = element_rect(color="white", fill="white")
  )

@@

## Example count plots for explanation

(will be something nicer soon)

@@

@@

## Diversity

@@

divyearplot(festgenrevecs  %>% mutate(target=exdiv),ex=NULL, yl="External genre diversity", convert=convertplots, networkstats = F)
divyearplot(festgenrevecs  %>% mutate(target=exdiv, lower=elower, upper=eupper), 
            ex=exgenfests, yl="External genre diversity", convert=convertplots, splitab=F, networkstats = F)

@@

@@

@@

g=ggplot(festrolevecs, mapping=aes(ratiopf, ratiodf, color=ratiof, shape=ab, size=ab, text=tool))+
  geom_vline(xintercept = 0.5)+
  geom_hline(yintercept = 0.5)+
  geom_point()+
  scale_size_manual(values =c(1.4,0.8)*1.2, guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype")+
  scale_color_gradientn(colours =rolecols, name="Female\nto male\nratio\namong\nproducers\n&directors", limits=c(0,1))+
  theme_bw()+
  theme(#legend.position = 'none',
        plot.background = element_rect( fill="white")
  )+
  labs(x="Producers", y="Directors")
  NULL

@@

@@

Note the intervals are different here, being the min-max calculated based on the number of unknown/unidentifiable/unisex first names among directors and producers in a given festival. They are not the same as the 95% bootstrapped confidence intervals, and therefore less conservative.

>>>>

abcols= divergingx_hcl(6, palette="Zissou 1")[c(1,5)] %>% c("gray70")
abshapes=c(16,4)

@@

  if(!splitab & !is.null(ex)){
   if(networkstats){
      fromy=2014.5; toy=2019.5
    } else{
      fromy=2008; toy=2022
      g=g+geom_errorbar(aes(ymin=lower, ymax=upper), color="gray40", width=0.1, size=0.45)
    }
    g=
      g+facet_wrap(~libelleFestival_NEW_VZ, nrow = ceiling(length(ex)/6))+
      # geom_point( aes(YearEvent, target),data=vecs %>% select(-libelleFestival_NEW_VZ), inherit.aes = F,
      #             color="gray90", size=0.9)+
      geom_line(data=vex %>% filter(YearEvent>fromy, YearEvent<toy) %>% 
                  group_by(YearEvent, libelleFestival_NEW_VZ) %>% 
                  summarise(target=mean(target, na.rm=T), tool=NA, ab=ab[1]), 
                color="gray60", size=0.3
                )+
      geom_point(data=vex, alpha=1, size=1.5, shape=16)+
      scale_x_continuous(breaks=seq(2009,2021,3) )+
      scale_y_continuous(limits=c( min(vecs$target), max(vecs$target) ))+
      theme(
       panel.grid.major.x  = element_line(color="gray95"),
       panel.grid.minor.x  = element_blank(),
       legend.position = 'none'
       )
  }

@@

sysplots = function(sysdiv, yl){
  g=  ggplot(sysdiv,aes(YearEvent, sysdiv, color=ab))+
    geom_line(position=position_dodge(width = 0.2))+
    geom_errorbar(aes(ymin=slower, ymax=supper),width=0.1, linewidth=0.45,position=position_dodge(width = 0.2) )+
    scale_x_continuous(breaks=2012:2021)+
    scale_color_manual(values=c(abcols))+
    theme_bw()+
    theme(legend.position = 'none')+
    theme(
      panel.grid.minor.x  = element_blank(),
       panel.grid.minor.y  = element_blank(),
      plot.background = element_rect(color="white", fill="white"),
      axis.title.x = element_blank()
    )+
    labs(y=yl)
 return(g)
}

@@

# big force directed, use that.
gr = as_tbl_graph(graph_from_data_frame(e2, directed = F, vertices = nodelist %>% filter(EventID_VZ %in% c(e2$from,e2$to))))
g = ggraph(gr  ) +
  geom_node_point(aes(color=YearEvent, size=nf)) +
  #geom_node_text(aes(label=name)) +
  geom_edge_arc(aes(color=coloryear, alpha=dist),  width=0.1, strength=0.04) +
  scale_color_viridis(end=0.9)+
  scale_edge_color_viridis(end=0.9)+
  scale_edge_alpha(range=c(0.15, 0.5))+
  scale_size(0.5, 1.5)+
  theme_void()+
  theme(legend.position = 'none',
        plot.background = element_rect(color="white", fill="white")
  )

@@

@@

# Pipeline plots

@@

## * Diversity

@@

sysplots(attr(festgenrevecs,"sysdivs"), yl="System internal genre diversity")

divyearplot(festgenrevecs  %>% mutate(target=exdiv),ex=NULL, yl="External genre diversity", convert=convertplots, networkstats = F)

divyearplot(festgenrevecs  %>% mutate(target=exdiv, lower=elower, upper=eupper), 
            ex=exgenfests, yl="External genre diversity", convert=convertplots, splitab=F, networkstats = F)

@@

sysplots(attr(festlangvecs,"sysdivs"), yl="System internal language diversity")

@@

sysplots(attr(festcountryvecs,"sysdivs"), yl="System internal geo diversity")

@@

g=ggplot(festrolevecs, mapping=aes(ratiopf, ratiodf, color=ratiof, shape=ab, size=ab, text=tool))+
  geom_vline(xintercept = 0.5)+
  geom_hline(yintercept = 0.5)+
  geom_point()+
  scale_size_manual(values =c(1.4,0.8)*1.2, guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype")+
  scale_color_gradientn(colours =rolecols, name="Female\nto male\nratio\namong\nproducers\n&directors", limits=c(0,1))+
  theme_bw()+
  theme(#legend.position = 'none',
        plot.background = element_rect( fill="white")
  )+
  labs(x="Producers", y="Directors")+
  NULL

@@

sysplots(attr(festrolevecs,"sysdivs"), yl="System-wide weighted F2M ratios")+lims(y=c(0,1))

@@

Note the intervals are different here, being the min-max calculated based on the number of unknown/unidentifiable/unisex first names among directors and producers in a given festival. They are not the same as the 95% bootstrapped confidence intervals, and therefore less conservative, but give an idea of the range the true ratio may lie in if we could identify all names.

Maybe should still also do the bootstrapped intervals here, and somehow take into account the min/max unidentified - some entries like the last Hot Docs are very small, so the ratio is not super reliable.
